---
title: "CaseStudy1_GDP"
author: "Vivek Bejugama"
date: "October 27, 2016"
output: 
  html_document:
    keep_md: true
---

##Intoduction:
The following is the end-to-end(downloading data to reporting) analysis of countires GDP vs their respective income groups classifications. 

```{r}
#Initializing the project variables:
rootDir <- "C://Users//vivek//Documents//R//R_Projects//CaseStudy1_GDP"
fileDir <- ".//Data_Files"
scriptDir <- ".//Scripts"
setwd(rootDir)
```

##DownLoading and Preparing tidy-data for analysis
Gathering the raw data from The World Bank website.
GDP - http://data.worldbank.org/data-catalog/GDP-ranking-table
Education - http://data.worldbank.org/data-catalog/ed-stats
```{r}
#Moving to the scirpts directory
setwd(rootDir)
setwd(scriptDir)

# calling the Data downloding script
source("Data_Gather.R", echo =T, keep.source = T,  max.deparse.length = 500)   
```

Creating a final clean merged dataset 
```{r}
#Moving to the scirpts directory
setwd(rootDir)
setwd(scriptDir) 

# Calling the Data Preparation script
source("Data_Prep.R", echo =T, keep.source = T, max.deparse.length = 500)
```

##Analysis of the merged clean Data frames
a. No. of missing matches  
b. Sorting the merged Data Frame ascending order of GDP.
c. 13th Country in the sorted data
d. Average GDP rankings for the "high income: OECD" and "High income: non OECD" gorups
```{r}
#Moving to the scirpts directory
setwd(rootDir)
setwd(scriptDir) 

# Calling the Data Analysis script
source("Data_Analysis.R", echo =T, keep.source = T,  max.deparse.length = 500)
```

##Ploting the GDP vs income group
a. Plot of all countires by income groups seperated by differnt colours
```{r}
#Moving to the scirpts directory
setwd(rootDir)
setwd(scriptDir) 

# Calling the Data Plot script
source("Data_Present.R", echo =T, keep.source = T, max.deparse.length = 500)
```

##Dividing the data into 5 Quartile Gorups.
a. GDP ranking divided into 5 quartile groups
```{r}
#Moving to the scirpts directory
setwd(rootDir)
setwd(scriptDir) 

# Calling the Data Analysis script
source("Data_Quantile.R", echo =T, keep.source = T, max.deparse.length = 500)
```

##Conclusion
From the above analysis we see we have about 5 countries thought they fall under lower middle income by income group they are still in top 20 percentile. 
The GDP is highly right skeewed for each income group suggesting there are few countries in each income group having way more GDP than rest in the group. 
High income:OECD member group have slightly greater mean and lower varience than the rest of the group.
Since this is an observational study we can not define cause and effect for the income level group and the GDP of the country.




